Jackknife

### 2021-02-23 analysis/rev_prototyping/jackknife.Rmd
fia small jks

fia_to_jk <- sample(fia_sites$site, size = 100, replace = F)

@@

fia_small_to_jk <- sample(fia_small_sites$site, size = 100, replace = F)

fia_small <- filter(fia_small, site %in% fia_small)

>>>>

fia_to_jk <- sample(fia_sites$site, size = nrow(fia_sites), replace = F)

fia_to_jk <- fia_to_jk[1:1000]

@@

fia_small_to_jk <- sample(fia_small_sites$site, size = nrow(fia_small_sites), replace = F)

fia_small_to_jk <- fia_small_to_jk[1:1000]

fia_small <- filter(fia_small, site %in% fia_small_to_jk)
